\LARGE \bf Detection of design pattern : A systematic mapping study

### 2016-01-02 article/main.tex
modified:   main.tex

A conclusion section

>>>>

In this paper we conducted a systematic mapping study to get an overview on existing research on design pattern detection. We queried Scopus database that indexes multiple sources (IEEE,ACM,SPRINGER and other) and we identified 55 article between 2000 and 2015 that are relevant to our study. We collected all the articles after querying the database, then we screened them using their title, abstract and keywords to ensure that they were relevant to our work. Finally we analyzed every one of the included article to classify them according to our classification scheme.
Interest on the detection of design pattern has been growing increasingly since 2003, but the field began to lose its interest after 2010.
In response to RQ1, the filed of design pattern detection still suffers from a lack of maturity 
(Section IV J) and it's clear that the domain  still has some way to go, to reach the necessary maturity. It would be interesting to have more experiments and real benchmarks to help  standardizing and evaluating design pattern detection tools.
